On Secure Delegation of SampBQP with a Classical Client

### 2020-02-06 bqp.tex
Begin implementing changes from the Skype meeting

In this section we present our constant-round blind delegation protocol for $\BQP$.
We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.

\begin{thm}
	There exists a constant-round and blind $\QPIP_0$ protocol with a classical client for $\BQP$ with negligible completeness and soundness.
\end{thm}

We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.

Let $L\in\BQP$, and $x\in\set{0,1}^*$.

There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
In fact, they have the same certificate $\ket{\psi_x}$ with some inverse polynomial gap between the completeness and soundness parameters.
See the excellent text \cite{kitaev2002classical} for details.
According to \cite{PhysRevA.93.022326}, the certificate can be check using only $X$ and $Z$ measurements.
We'll also summarize said proofs in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.

\begin{thm}
	\protoref{BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

\begin{protocol}{Protocol for $\BQP$}
	\label{proto:BQP}
	Let $n$ be the number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	\begin{enumerate}
		\item The verifier sends $x$ to the prover
		\item The honest prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{enumerate}
\end{protocol}

Now we compile \cref{proto:BQP} using $\mathsf{QHE}$ in order to achieve blindness.
We denote the honest prover's action in \cref{proto:BQP} as $\cF$; that is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $\lambda$ be the security parameter.
	Let $L$ be the depth of the circuit corresponding to $\cF$.
	Let $n$ be number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	\begin{enumerate}
		\item The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
		\item The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
		\item The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\item The verifier measures the incoming ciphertext according to \cref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates \Ethan{Not sure if rigorous enough}
		\item The verifier decodes the measurement results
		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\protoref{BlindBQP} has negligible completeness in both $T$ and $\lambda$
\end{thm}
\begin{proof}
	Based on the correctness of $\mathsf{QHE}$, the verifier would successfully decode $\cF(c)$ with overwhelming probability.
	The subsequent underlying QMA check also has overwhelming probability of acceptance.
\end{proof}

\begin{thm}
	\protoref{BlindBQP} has negligible soundness in both $T$ and $\lambda$
\end{thm}
\begin{proof}
	The verifier's actions is equivalent to first decoding the prover's message then measuring it.

	Suppose the prover's message decodes to some $\rho$. Since it is a quantum state, the soundness of the underlying $\QMA$ instance can be used.

	That is, there doesn't exists a valid certificate $\rho$ that has non-negligible probability of acceptance.
\end{proof}

\begin{thm}
	\protoref{BlindBQP} is IND-CPA
\end{thm}
\begin{proof}
	The only thing the prover learns is $c$ and $pk$, so this follows directly from $\mathsf{QHE}$'s security.
\end{proof}

Now we can simply apply the following results from \cite{parallelrep} to obtain a blind and constant-round for $\QPIP_0$ with negligible completeness and soundness.
\begin{thm}
	There is a compiler that takes a $\QPIP_1$ protocol with the following properties:
	\begin{itemize}
		\item classical inputs
		\item client uses only X/Z measurements
		\item negl. completeness and soundness
	\end{itemize}
	and outputs a corresponding $\QPIP_0$ protocol with negl. completeness and soundness \Ethan{same inputs...?}
\end{thm}

\begin{rmk}
	The same construction works for $\FBQP$ too.
	\Ethan{Maybe say more? Where should I define $\FBQP$?}
\end{rmk}

>>>>

In this section we present our constant-round blind delegation protocol for $\BQP$. That is, proving this theorem:
\begin{thm}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
We'll spend this section construct said protocol piece by piece, starting with the following $\QPIP_1$ protocol for $\BQP$.
We'll later construct a protocol for $\SampBQP$ following the same flow of logic, albeit requiring more careful analysis.

Let $L\in\BQP$, and $x\in\set{0,1}^n$.
We start with an overview of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.
We'll summarize some more relevant details of this construction in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.

\begin{protocol}{Verifying yes-instances for $\BQP$}
	\label{proto:BQP}
	\begin{enumerate}
		\item The verifier chooses some tensor product of $X$ and $Z$ measurements $\Lambda$
		\item The prover sends the verifier some state $\rho\in\cB^{\otimes m}$ qubit-by-qubit.
		\item The verifier measures $\rho$ according to $S$
		\item The verifier decides whether to accept based on the measurement results.
	\end{enumerate}
\end{protocol}

\cref{proto:BQP} has negligible completeness and soundness. \Ethan{Elaborate or no?}

Now we compile \cref{proto:BQP} using $\mathsf{QHE}$ in order to achieve blindness.
We denote the honest prover's action in \cref{proto:BQP} as $\cF$.

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $d$ be the depth of the circuit corresponding to $\cF$.
	\begin{enumerate}
		\item The verifier chooses $\Lambda$ and computes $\Lambda'$ using \cref{decodeMeasureOrder}
		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
		\item The verifier computes $c=\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $c$ and $evk$ to the prover
		\item The prover computes $\mathsf{QHE.Eval}(\cF, c)$ and sends it to the verifier qubit-by-qubit.
		\item The verifier measures the incoming ciphertext according to $\Lambda'$
		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to the measurement results
		\item The verifier decides whether to accept based on \cref{proto:BQP}
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\cref{proto:BlindBQP} preserves the completeness and soundness of \cref{proto:BQP}
\end{thm}
\begin{proof}
	Based on the correctness of $\mathsf{QHE}$, any prover strategy in \cref{proto:BlindBQP} has a corresponding strategy in \cref{proto:BQP}.
\end{proof}

\begin{thm}
	\cref{proto:BlindBQP} is IND-CPA secure.
\end{thm}
\begin{proof}
	The only thing the prover sees is $c$ and $evk$, so this follows directly from $\mathsf{QHE}$'s security.
\end{proof}

Mahadev's protocol compiles QPIP1 to QPIP0 but deteriorates soundness, and \cite{parallelrep} says parallel repetition works to recover good soundness guarantees.
\Ethan{TODO elaborate}

\begin{rmk}
	Our protocol for $\BQP$ can easily be generalized to $\FBQP$ too in the following way:
	\Ethan{TODO actually need 2 copies per bit now}
\end{rmk}
